Context-dependent consequences of including lagged effects in demographic models

### 2022-03-07 docs/paper.Rmd
transfer notes from meeting with Emilio

---
title: "Full Title"
shorttitle: "Running Title"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false

@@

Introduction with an in-text citation [@scottInteractiveEffectsDrought2019].

>>>>

---
title: "Context-dependent consequences of including lagged effects in demographic models"
shorttitle: "Lagged Effects IPMs"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false

@@

1.  Demographic models are widely used for all kinds of stuff

2.  It has long been recognized that there is the potential for lagged effects.
    Now there's evidence for that [@scottInteractiveEffectsDrought2019].

3.  Lagged effects could be different in different habitat types (and this could be a big reason for differences between habitats)
